---
title: "Coding"
author: "Yongjun Kwon"
date: "2/14/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## 1) Machine Learning


```{r}
library(tidyverse)
library(tree)
library(randomForest)
library(stringr)
```

a) Performance?

Performance would be how accurate resulted prediction would be to the real life examples. This can usually be assessed by using a number of methods such as, a confusion matrix, ROC curve, and etc.

b) Splitting data

```{r}
geneD<-read_csv("gene data.csv", col_names=T)
set.seed(2)
train<-sample(1:nrow(geneD),(nrow(geneD)/2))
```

geneD.ts<-geneD[-train,]
geneD.count<-as.factor(Class)[-train]
tree.geneD<-tree(as.factor(Class) ~.,geneD,subset=train)
tree.pred<-predict(tree.geneD,geneD.ts,type = "class")
table(tree.pred,geneD.count)

c) Logistic regression of the data
```{r}
glm.geneD<-glm(as.factor(Class)~.,data=geneD, family=binomial)
summary(glm.geneD)
pred.geneD<-predict(glm.geneD,type="response")
```

d) Random Forest
```{r}
rf.geneD<-randomForest(as.factor(Class) ~.,data=geneD,subset=train,mtry=12, importance=TRUE)
rf.geneD


```
\newpage

##2) Hamming Distance

```{r}
string1<-c("Eagle")
string2<-c("Eager")

string1<-gsub("S","Z",string1)
string1<-gsub("s","z",string1)
string2<-gsub("S","Z",string2)
string2<-gsub("s","z",string2)

#first letter check
fstr1<-tolower(substr(string1,1,1))
fstr2<-tolower(substr(string2,1,1))

#splitting/counting the first string
split_str1<-str_split(string1,"",simplify=T)
count_str1<-nchar(string1)

hammdist<-0


if (fstr1==fstr2)
{
  hammdist<-hammdist+0
  
  for(x in 2:count_str1)
  {
    str1<-substr(string1,x,x)
    str2<-substr(string2,x,x)
    if (str1==str2)
      {
        hammdist<-hammdist+0 }
      else if (str_detect(str1,"[[:upper:]]")!=str_detect(str2,"[[:upper:]]"))
        {
        hammdist<-hammdist+0.5
        
        }   
      else {hammdist<-hammdist+1}
  }
} else { 
  
  hammdist<-hammdist+1
  for (x in 2:count_str1)
  {
    str1<-substr(string1,x,x)
    str2<-substr(string2,x,x)
    if (str1==str2)
      {
        hammdist<-hammdist+0 }
      else if (str_detect(str1,"[[:upper:]]")!=str_detect(str2,"[[:upper:]]"))
        {
        hammdist<-hammdist+0.5
        
        }   
      else {hammdist<-hammdist+1}
   }    
  }
  
paste ("Calculated Hamming distance is ",hammdist)

```
a)	"data Science" to  "Data Sciency"
```{r}
string1<-c("data Science")
string2<-c("Data Sciency")

string1<-gsub("S","Z",string1)
string1<-gsub("s","z",string1)
string2<-gsub("S","Z",string2)
string2<-gsub("s","z",string2)

#first letter check
fstr1<-tolower(substr(string1,1,1))
fstr2<-tolower(substr(string2,1,1))

#splitting/counting the first string
split_str1<-str_split(string1,"",simplify=T)
count_str1<-nchar(string1)

hammdist<-0


if (fstr1==fstr2)
{
  hammdist<-hammdist+0
  
  for(x in 2:count_str1)
  {
    str1<-substr(string1,x,x)
    str2<-substr(string2,x,x)
    if (str1==str2)
      {
        hammdist<-hammdist+0 }
      else if (str_detect(str1,"[[:upper:]]")!=str_detect(str2,"[[:upper:]]"))
        {
        hammdist<-hammdist+0.5
        
        }   
      else {hammdist<-hammdist+1}
  }
} else { 
  
  hammdist<-hammdist+1
  for (x in 2:count_str1)
  {
    str1<-substr(string1,x,x)
    str2<-substr(string2,x,x)
    if (str1==str2)
      {
        hammdist<-hammdist+0 }
      else if (str_detect(str1,"[[:upper:]]")!=str_detect(str2,"[[:upper:]]"))
        {
        hammdist<-hammdist+0.5
        
        }   
      else {hammdist<-hammdist+1}
   }    
  }
  
paste ("Calculated Hamming distance is ",hammdist)
```
b)	"organizing" to "orGanising"
```{r}
string1<-c("organizing")
string2<-c("orGanising")

string1<-gsub("S","Z",string1)
string1<-gsub("s","z",string1)
string2<-gsub("S","Z",string2)
string2<-gsub("s","z",string2)

#first letter check
fstr1<-tolower(substr(string1,1,1))
fstr2<-tolower(substr(string2,1,1))

#splitting/counting the first string
split_str1<-str_split(string1,"",simplify=T)
count_str1<-nchar(string1)

hammdist<-0


if (fstr1==fstr2)
{
  hammdist<-hammdist+0
  
  for(x in 2:count_str1)
  {
    str1<-substr(string1,x,x)
    str2<-substr(string2,x,x)
    if (str1==str2)
      {
        hammdist<-hammdist+0 }
      else if (str_detect(str1,"[[:upper:]]")!=str_detect(str2,"[[:upper:]]"))
        {
        hammdist<-hammdist+0.5
        
        }   
      else {hammdist<-hammdist+1}
  }
} else { 
  
  hammdist<-hammdist+1
  for (x in 2:count_str1)
  {
    str1<-substr(string1,x,x)
    str2<-substr(string2,x,x)
    if (str1==str2)
      {
        hammdist<-hammdist+0 }
      else if (str_detect(str1,"[[:upper:]]")!=str_detect(str2,"[[:upper:]]"))
        {
        hammdist<-hammdist+0.5
        
        }   
      else {hammdist<-hammdist+1}
   }    
  }
  
paste ("Calculated Hamming distance is ",hammdist)
```
c)	"AGPRklafsdyweIllIIgEnXuTggzF" to "AgpRkliFZdiweIllIIgENXUTygSF")
```{r}
string1<-c("AGPRklafsdyweIllIIgEnXuTggzF")
string2<-c("AgpRkliFZdiweIllIIgENXUTygSF")

string1<-gsub("S","Z",string1)
string1<-gsub("s","z",string1)
string2<-gsub("S","Z",string2)
string2<-gsub("s","z",string2)

#first letter check
fstr1<-tolower(substr(string1,1,1))
fstr2<-tolower(substr(string2,1,1))

#splitting/counting the first string
split_str1<-str_split(string1,"",simplify=T)
count_str1<-nchar(string1)

hammdist<-0


if (fstr1==fstr2)
{
  hammdist<-hammdist+0
  
  for(x in 2:count_str1)
  {
    str1<-substr(string1,x,x)
    str2<-substr(string2,x,x)
    if (str1==str2)
      {
        hammdist<-hammdist+0 }
      else if (str_detect(str1,"[[:upper:]]")!=str_detect(str2,"[[:upper:]]"))
        {
        hammdist<-hammdist+0.5
        
        }   
      else {hammdist<-hammdist+1}
  }
} else { 
  
  hammdist<-hammdist+1
  for (x in 2:count_str1)
  {
    str1<-substr(string1,x,x)
    str2<-substr(string2,x,x)
    if (str1==str2)
      {
        hammdist<-hammdist+0 }
      else if (str_detect(str1,"[[:upper:]]")!=str_detect(str2,"[[:upper:]]"))
        {
        hammdist<-hammdist+0.5
        
        }   
      else {hammdist<-hammdist+1}
   }    
  }
  
paste ("Calculated Hamming distance is ",hammdist)
```


d)	Describe a scenario (3-4 sentences) where implementing the standard Hamming distance algorithm would be applicable. 

This can be used to assess the distance between two query sequences to determine their similarity scores

\nextpage

## 3. Data Cleaning

```{r}
patentd<-read_csv("patent_drawing data.csv",col_names = T)
```

a) 

```{r}
i<-str_count(patentd$text,".*embod.*")
sum(i)
```

b) 

```{r}
i<-str_count(patentd$text,".*embod.*invention.*")
sum(i)

```


\newpage
