---
title: "Marray material"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown Presentation Prep.

Loading the data onto R
```{r}
library(rentrez);library(ape);library(gplots);library(RColorBrewer);library(ggplot2);library(ggfortify)
JARA<-read.table("JARAAnalysisTab.txt",sep = "\t",header = TRUE)
```

kmeans with 2 diff cluster based on signal strength
```{r}
JARA.sig<-data.frame(JARA[,9],JARA[,10])
cl<-kmeans(JARA.sig,2)
plot(JARA.sig,col=cl$cluster)

```

hclust with euclidian method based on signal strength
```{r}
x<-c(JARA[,9],JARA[,10])
sl.out<-hclust(dist(x,method="euclidian"),method="single")
plot(sl.out,lwd=0.4,col.axis="brown",col="magenta",ylab="Distance",xlab="Clusters",hang=-1,main=NA,sub=NA,axes=FALSE)
```

stripchart based on signal strength
```{r}
stripchart(JARA.sel,method = "jitter",cex.lab=1.5,vertical=TRUE,col=c("red","darkgreen"),xlab=NA,ylab="Signal Strength")

```

heatmap generated based on signal strength
```{r}
heatmap.2(as.matrix(JARA.sel),scale="none",col=greenred(75),dendrogram = "row",key=TRUE,symkey = FALSE,density.info = "none",trace="none",cexRow=0.1,cexCol = 0.5)
```



heatmap generated based on z score
```{r}
JARA.z<-as.data.frame(JARA[,13:14])

heatmap.2(as.matrix(JARA.z),scale="none",col=greenred(75),dendrogram = "none",key=TRUE,symkey = FALSE,density.info = "none",trace="none",cexRow=0.1,cexCol = 0.5)
```

picking top 400 signal strength and running kmeans clustering
```{r}
JARA400<-JARA.sel[1:400,]
cl<-kmeans(JARA400,2)
plot(JARA400,col=cl$cluster)
points(cl$centers,col=1:2,pch=8,cex=2)

```


rentrez package
install.packages("rentrez")
```{r}
testvector<-JARA[2:3,1]
x<-as.data.frame(testvector)
class(testvector)
testvector<-JARA[2,1]
x
x<-as.data.frame(testvector)
x
entrez_fetch(db="pubmed",id=JARA[2:3,1],rettype = "abstract",retmode="")

```

## xxxxxxxxx



```{r}


```
